\documentclass[12pt]{article}

\usepackage{tikz}
\usepackage{slashbox}
\usepackage{caption}
\usetikzlibrary{automata, positioning}
\begin{document}
	\begin{enumerate}
	\item
	The state diagram is like below:
	
	\begin{tikzpicture}[shorten >=1pt,node distance=2cm,on grid,auto] 
    	\node[state,initial] (11) {11}; 
    	\node[state] (10) [above right=of 11] {10}; 
    	\node[state] (00) [below right=of 11] {00}; 
    	\node[state](01)  [above right=of 00] {01};
    	\path [->]
    	(11) edge node {1} (10)
    	     edge [loop above] node {0} ()
    	(10) edge node {1} (01)
    	     edge [loop above] node {0} ()
    	(01) edge node {1} (00)
    	     edge [loop above] node {0} ()
    	(00) edge node {1} (11)
    	     edge [loop above] node {0} ();    	         
	\end{tikzpicture}	
	
	The state table is like the following:
	
	\begin{tabular}{c|cc}

		$x$ & Current State & Next State\\ \hline
		0 & 00 & 00\\ 
		0 & 01 & 01\\ 
		0 & 10 & 10\\ 
		0 & 11 & 11\\ 		
		1 & 00 & 11\\ 
		1 & 01 & 00\\ 
		1 & 10 & 01\\ 
		1 & 11 & 10\\ 
	\end{tabular}
	\begin{center}
	

	\begin{tabular}{|c|c|c|c|c|}
	\hline
	\backslashbox{x}{Current State} & 00 & 01 & 11 & 10 \\ \hline
	0 &0&0&1&1\\ \hline
	1 &1&0&1&0\\ \hline

	\end{tabular}		
	\end{center}
	\captionof{table}{Karnugh Map for $D_2$}		
	
	
	\begin{center}
	\begin{tabular}{|c|c|c|c|c|}
	\hline
	\backslashbox{x}{Current State} & 00 & 01 & 11 & 10 \\ \hline
	0 &0&1&1&0\\ \hline
	1 &1&0&0&1\\ \hline

	\end{tabular}		
	\end{center}
	\captionof{table}{Karnugh Map for $D_2$}
	\item
		\begin{enumerate}
		\item
		1- Capacity of the memory.
		2- Speed of the memory.
		3- Cost of the memory.
		\item
		We use memory hierarchy to have the maximum capacity and speed and minimum cost. The method is that you use memories with higher speed in the place in which they are closer to the CPU and memories with less speed but more capacity further from the CPU. To have maximum speed and capacity and minimum cost.
		\item
		Yes, it's possible. When the cost of retrieving data from the bottom of the hierarchy to the topper level of hierarchy is more than cost of buying more memory from the type of the top of hierarchy. 
		\item
		Static memories are more expensive and have high speed because they don't need refreshing and less dense and they use less power. But Dynamic memories are chipper but they need refresher and so they are slower than static memories and they are denser than static memories and they use more power. - Using static memories is easier.
		\end{enumerate}
		\item
		\begin{enumerate}
		\item
		$T_{access}=t_1+(1-h_1)(t_2+(1-h_2)(t_3+(1-h_3)t)))=$		
		\item
		\end{enumerate}
		\item

		
	\end{enumerate}
	
\end{document}